---
title: "TAE Submission 6"
---


First, we prepare the working environment.
```{r}
rm(list=ls())
```

# Data preparation

Load the tweets

Ensure stringsAsFactors is set to FALSE to prevent character vectors being converted into factors
```{r}
twitter_train <- read.csv("train.csv", stringsAsFactors = FALSE)
twitter_test <- read.csv("test.csv", stringsAsFactors = FALSE)

#str(twitter_train)
# 22500 obs
```

Analyze train dataset

Predictions:
1 - negative
2 - neutral
3 - positive

```{r}
table(twitter_train$sentiment)
```
6788 negative, 7900 neutral and 7812 positive

# Pre-processing

Create DTM

```{r}
if(!require(tm)){
  install.packages("tm")
  library(tm)
}
if(!require(SnowballC)){
  install.packages("SnowballC")
  library(SnowballC)
}

corpus <- Corpus(VectorSource(twitter_train$tweet))
```

Check elements of the corpus

```{r}
as.character(corpus[[1]])
as.character(corpus[[5625]])
as.character(corpus[[11250]])
as.character(corpus[[16875]])
as.character(corpus[[22500]])
```

1st: convert to lower case
2nd: remove stopwords
3rd: remove punctuation
4th: remove numbers
5th: stemming
6th: remove highly relevant words -> words describing weather taken from (https://usefulenglish.ru/vocabulary/weather-and-temperature)
7th: remove sparse terms (do later/next iteration)

```{r}
corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, stemDocument)
corpus <- tm_map(corpus, removeWords, c("weather", "thunderstorm", "sun", "rain", "cloud", "wet", "humid", "rain", "wind", "fog", "storm", "dry", "arid", "frigid", "breeze",  "cold", "hot", "warm", "overcast", "dark", "hail", "sky", "cool", "snow", "freeze", "clear", "summer", "thunder", "spring", "flood", "sky"))
```

Check the output of the pre-processing

```{r}
as.character(corpus[[1]])
as.character(corpus[[5625]])
as.character(corpus[[11250]])
as.character(corpus[[16875]])
as.character(corpus[[22500]])
```

# Create DTM

```{r}
dtm <- DocumentTermMatrix(corpus)
```


```{r}
#dtm[1,]
inspect(dtm[1,])
inspect(dtm[5625,])
inspect(dtm[11250,])
inspect(dtm[16875,])
inspect(dtm[22500,])
```

Remove sparse terms

```{r}
dtm <- removeSparseTerms(dtm, 0.995)
dtm
```

Now the dtm is a 22500 document by 204 term matrix

# Prepare DTM for model learning

First, we prepare the dataframe and column names

```{r}
twittersparse <- as.data.frame(as.matrix(dtm))
colnames(twittersparse) <- make.names(colnames(twittersparse))
```

Next, we add the output variable (1 = negative, 2 = neutral and 3 = positive) for the 'twittersparse' dataframe.

```{r}
twittersparse$sentiment <- twitter_train$sentiment
twittersparse$sentiment <- as.factor(twittersparse$sentiment)
#str(twittersparse)
#head(twittersparse)
```

# Train and test a classifier
# Classifier: Random Forest

Takes approx. 19 minutes to train

```{r}
library(randomForest)

modelRF <- randomForest(sentiment ~., data = twittersparse) 

modelRF
```

Prediction

```{r}
predictRF <- predict(modelRF, newdata = twittersparse, type="class")
table(predictRF, twittersparse$sentiment)
acc <- (6206+7118+7071)/nrow(twittersparse)
acc # 0.9064444
```

# Actual Prediction

Prepare the test dataset into a DTM of similar columns as the training dataset

```{r}
corpus <- Corpus(VectorSource(twitter_test$tweet))

corpus <- tm_map(corpus, content_transformer(tolower))
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, stemDocument)
corpus <- tm_map(corpus, removeWords, c("weather", "thunderstorm", "sun", "rain", "cloud", "wet", "humid", "rain", "wind", "fog", "storm", "dry", "arid", "frigid", "breeze",  "cold", "hot", "warm", "overcast", "dark", "hail", "sky", "cool", "snow", "freeze", "clear", "summer", "thunder", "spring", "flood", "sky"))

dtm <- DocumentTermMatrix(corpus)

twittersparse_actual <- as.data.frame(as.matrix(dtm))
colnames(twittersparse_actual) <- make.names(colnames(twittersparse_actual))
twittersparse_actual <- twittersparse_actual[colnames(twittersparse_actual) %in% colnames(twittersparse)]

#twittersparse_actual$sentiment <- 0

#col_order <- colnames(twittersparse)
#twittersparse_actual <- twittersparse_actual[, col_order]
```

Make predictions on the test dataset

```{r}
predictRF_actual <- predict(modelRF, newdata = twittersparse_actual, type = "class")
twitter_test$sentiment <- predictRF_actual
```

Prepare results for exporting to a csv file.

```{r}
twitter_final_pred <- twitter_test[, c("id", "sentiment")]

write.csv(twitter_final_pred, "C:\\Users\\hakim\\Documents\\SUTD\\SUTD Term 6\\TAE\\Competition\\Submission_6.csv", row.names = FALSE)
```

